The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2010-06-02 script/en/chapters/authors.tex
Added another kid book

\item[\textrm{[Harder2003]}] \index{Harder 2003}
    Corinna Harder und Jens Schumacher, \\
    {\em Top secret. The big book for detectives (original title: 
     Streng geheim. Das gro\ss e Buch der Detektive)}, Moses, 2003. \\

>>>>

\item[\textrm{[Harder2003]}] \index{Harder 2003}
    Corinna Harder and Jens Schumacher, \\
    {\em Top secret. The big book for detectives (original title: 
     Streng geheim. Das gro\ss e Buch der Detektive)}, Moses, 2003. \\

\item[\textrm{[Talke-Baisch2003]}] \index{Talke-Baisch 2003}
    Helga Talke and Milena Baisch, \\
    {\em Your mission in the weird villa. Riddle thriller (original title: 
    Dein Auftrag in der unheimlichen Villa. Kennwort R\"atselkrimi)},
    Loewe, 2003. \\
    From 4th form, ~~~\url{http://www.antolin.de}\\
%    \url{http://www.antolin.de/all/bookdetail.jsp;jsessionid=abcexNCPR6tzlcM5FZpDs?book_id=16224}\\
    Young detectives are faced simple ciphers and codes during their missions.\\
